Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-05-11 WRITEUP/ms.tex
revisde

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MCC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter
%mm (gas+stars),
    taking into account both gas and stars,
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish
%mm scrutinizing
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
As shown in the figure, MCCs of \flower lie along the locus of $A_V \simeq 8.9$ clouds observed by
\citet{Lombardi10a} in the MW.
Further discussions on the interpretation of this is provided in \Sec{MR}.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma$, $R$, $M_{\rm gas}$,
$\Sigma{\rm gas}$) with those of molecular gas structures from \obs at.
Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to
the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
Their velocity dispersions are also comparable to those observed in the inner
Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
locus of $\sigma\propto R^{0.56}$.
Such high velocity dispersions and surface densities can be explained partly because
these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest,
and also from the injection of kinetic energy from recent
\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2,
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun.
Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that
the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in
its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in
interpreting observational results is further discussed in the next subsection (\Sec{rot}).

@@

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
 % 
 Note that the bulk velocity dispersion $\sigma_{\rm bulk}$ is typically comparable to the non-thermal term $\sigma_{\rm NT}$, 
as the two are connected via the Euler equation, but this depends on the evolutionary stage of \flower (\Fig{vv}).
%
%\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field indicating that contribution from shear is unlikely to dominate the velocity dispersions of the smaller MCCs identified, especially at the highest $n_{\rm ncut}$.\label{ftn:veldisp}}.

% allss: 0.32
% In [13]: print(get_Mach_all_clouds(ss11))
%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
% allss: 18.96
%In [15]: print(get_Mach_all_clouds(ss12))
%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
%  5.05517168  6.93886988  5.4830306 ]
% see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We compare the gas velocity dispersion from bulk motions versus turbulent motions for MCCs in the accreting
and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
but a disk-like morphology in the quiescent phase
(see \Fig{MCC} and \Fig{MCC28}).
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
whereas the opposite is true in the quiescent phase. In addition, the two velocity dispersion terms are of the same order of magnitude.

We note that \citet{Behrendt16a} similarly concluded that large scale bulk motion may mimic turbulent velocity dispersion 
due to beam smearing even though the self-rotation of each individual sub-MCCs is washed out.

{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures
on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.

@@

In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
This makes sense from simply the fact that smaller MCCs have smaller masses.
However, what does it mean for them to lie on the same locus?
% is it what Jen's proposed? Or is it's just a result of $\rho\propto M R^{-3}$ (and $\rho$ is independent of R)
% and observational bias (selection effect due to projection in 2D, so $\rho \propto N_H R^{-1}$, where $N_H$ is a
% constant due to gas tracer) (i.e., middle and bottom panels of Fig 9 in BM02)?

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
regions of massive \SF.
%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
%  point on that relationship, at the constant $\Sigma$ value.  }
However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
with a certain tracer (e.g., \citealt{Ballesteros11}).
That is, it is solely a result of $\rho\propto M R^{-3}$.
For instance, \citet{Ballesteros02a} show that the density
of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
two-dimensional space, as is done in \obs.
When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
% since $M$ would then scale as $R^{3}$.
% naturally display a linear relationship in $\log M - \log R$ plot.

% the widespread in density for a given R.
We show the density-size relation ($\rho - R$) relation of MCCs of \flower in \Fig{rho}.
The interpretation of this figure is not that MCCs with small $R$ are found at high $n_{\rm cut}$ and large $R$ at low $n_{\rm cut}$, nor is that
the density of MCCs is independent of $R$. Rather, it is as we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold.
\DL{This is puzzling to me why we are seeing some really steep relationship between $\rho$ and $R$, almost $\rho \propto R^{-6}$
even though we are identifying the structures in 3D just like what BM02 did.}

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
\caption{Density and size of MCCs in the accreting phase of \flower.
At higher $n_{\rm cut}$, MCCs are broken into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
\AP{$\rho \rightarrow n$}
\label{fig:rho}}
\vspace{0.5em}
\end{figure}

@@

We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower,
and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}),
which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by
UV radiation and metal lines, and detailed stellar feedback.
Properties of \flower are briefly summarized in \Sec{sim}.
We use a three-dimensional clump-finding algorithm to identify MCCs and their sub-structures.
We decompose the molecular structures into non-overlapping objects by identifying a set of
density contours with varying cutoff densities at multiple evolutionary stages.
Most notably, the accreting phase, starburst phase, and quiescent phase.
We extract properties such as mass, size, Mach number, velocity
dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M},
\sigma, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
The $\sim$200\,pc-scale MCCs found with a low density threshold
correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
Overall, the mass of MCCs ranges between $10^{5.5-8.5}$\,\Msun, depending on the chosen density threshold.
This mass range is comparable to those observed in \z\ssim2 galaxies in rest-frame UV and optical wavelengths.
Similarly massive molecular structures (few times 10$^7$\,\Msun) have been
reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the
48\,kpc box studied by \citealt{Behrendt16a}).
However, the IGM and merger and accretion histories are not properly modeled in such simulations.
That said, the similar mass range found in MCCs of \flower\ is
reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
On the other hand, the gas velocity dispersion $\sigma$ is rather insensitive to the adopted density threshold.

@@

MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
These MCCs are, in fact, highly supersonic (with high Mach numbers).
Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma\simeq200$\,\kms); however,
comparing the velocity dispersions of MCCs from bulk motions versus turbulence
indicates that large-scale rotation is an important contributor, even in the
accreting phase of \flower, which displays a highly disturbed morphology.
This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date.
In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc)
should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
unless contributions from bulk motions are properly accounted for.
%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution
%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used
%for structures in the literature) are more turbulent based on solely measured velocity dispersion.

@@

% end
Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
While observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial,
we show in this work that prototypical galaxies at the EoR with properties similar to \flower
are expected to have molecular gas structures on sub-kpc scales; however, these are not
the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from
large-scale motions even in a highly disturbed stage.
This means that caution should be taken when interpreting observational data,
albeit the impressive resolution and sensitivity that are unprecedented.
%Careful consideration of large-scale motions is required
%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR.
It is thus currently unclear whether \highz molecular gas structures are truly intrinsically more turbulent than those in the local ISM.
This will become clearer in the next few years as deeper and higher resolution imaging of
molecular gas at \highz are observed with ALMA and NOrthern Extended Millimeter Array (NOEMA).
On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining
and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
%These predictions can in turn be
%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
%\SF since the cosmic dark ages.

>>>>

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCCs) using cosmological zoom-in simulation of a
$z\simeq 6$ prototypical galaxy (``\flower'').
%
We identify MCCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter 
to \obs.
%
In \flower, MCC masses are in the range of $10^{5.5-8.5}$\,\Msun, with sizes $R\lesssim200$\,pc. 
% 
We identify gravitationally unstable MCCs both via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis. 
MCCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
instability to % gravitational 
collapse.
%
Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
% 
We show that large-scale rotation is an important contributor to the velocity dispersion of MCCs, even in the highly disturbed phase of \flower, posing 
a challenge to the interpretation of molecular gas dynamics in \highz galaxies in the literature.
% Thus, velocity dispersions measured on similar scales (even down to 40\,pc) should not be taken as a direct 
% evidence that \highz molecular gas are intrinsically more turbulent than the local ISM, 
% unless contributions from bulk motions are properly accounted for.
% 
%Close resemblance of $Q_{\rm eff}$ and $Q_{\star}$ maps illustrates the importance of accounting for stellar contribution and disk thickness when 
%examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift 
%that are preferentially being observed now.
% 
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) on
$\lesssim$40\,pc are necessary to shed light on the star-forming gas dynamics since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

We show in \Fig{MR} the size-mass relation of the MCCs of \flower compared to observational data of molecular clouds associated with massive \SF in the
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870(R/{\rm pc})^{4/3} M_\odot$.
Motivated by \obs, we overplot lines of constants $A_V$ in the same plot.
Further discussions on the interpretation of this is provided in \Sec{MR}.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018F
%the $M_{\rm gas}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$,
$\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at.
Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to
the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms.
Their velocity dispersions are also comparable to those observed in the inner
Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the
locus of $\sigma_{\rm gas}\propto R^{0.56}$.
Such high velocity dispersions and surface densities can be explained partly because
these MCCs are located in the nuclear regions of the galaxy, where the potential well is the deepest,
and also from the injection of kinetic energy from recent
\SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}).
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2,
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun.
Furthermore, a comparison of the velocity dispersion from bulk motions versus that from turbulence (\Fig{vv}) suggests that
the high total velocity dispersion seen in the MCCs of \flower is partly a result of large-scale rotation, which is even more important in
its later stage of evolution as \flower is settling into a rotating disk galaxy. The implication of this in
interpreting observational results is further discussed in the next subsection (\Sec{rot}).

@@

The local sound speed of all identified molecular complexes is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e. $c_s^2 \ll \sigma_{\rm NT}^2$.
 In particular, the Mach number averaged on the the MCCs distribution at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.
% allss: 0.32
% In [13]: print(get_Mach_all_clouds(ss11))
%[10.62623949  3.10713402  7.0525831   3.336829   10.36052827  7.24157821
%  7.12323137  6.75282955  9.94086767  7.47769907  3.39894958  3.27304956
%  6.69290803 11.44844494  7.03862716  3.16574077  5.1015787   5.67749554
%  7.35946615  6.89475134  7.2433421  10.57019778 11.78414139  3.93499799
%  6.86173652  7.39686112  8.37197686  6.71749578  2.65304172  6.49617895
%  5.15095491  5.6606244   2.98923849  3.65475035  7.37703114  4.5669722
%  7.18720926  7.35017082  6.03000248  6.36373235 10.16701766  8.3894084
%  3.09284034  4.37994321  4.46497953  5.264101    8.11686     3.05183157
%  7.10365783  6.09513017  8.72517656  5.59659665  3.95290202  9.22726672
%  4.94960657  6.19757621  4.63335759  3.32670022  3.46706217  5.58358069
%  3.41808098  8.31386962  4.26357159  3.684986    4.01853538  3.62917357
%  6.05586465  9.82127908  6.68366736 11.0791874  13.28965621 10.42021747
%  3.04409362  7.21509021  3.63699627  8.12503492  3.20158298]
% allss: 18.96
%In [15]: print(get_Mach_all_clouds(ss12))
%[15.25049689  6.74580503  6.98246499  5.17070655  6.470997    7.02626558
%  4.42663778  6.34460542  4.90603266  3.66900884  4.03260414  6.9539893
%  8.36247744  4.89164338  4.12695121  6.55187227  6.15391173  3.56580625
%  5.74818066  3.81067175  6.65393948  9.10100946  6.35039889  4.78667156
%  5.05517168  6.93886988  5.4830306 ]
% see also e.g., test_brute/leaf_fields_ss16-28/18.96_10_fields/Mach_cloud-mass.png
% This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show the gas velocity dispersions from bulk motions versus turbulent motions for MCCs in the accreting
and quiescent phase in \Fig{vv}. We note that \flower displays a disturbed morphology in the accreting phase
but a disk-like morphology in the quiescent phase
(see \Fig{MCC} and \Fig{MCC28}).
Most MCCs in the accreting phase have turbulent velocity dispersions higher than the bulk motion velocity dispersions,
whereas the opposite is true in the quiescent phase. 
In addition, the two velocity dispersion terms are of the same order of magnitude. % as the two are connected via the Euler equation
{\em This indicates that gas velocity dispersions observed on similar physical scales and resolutions as presented here
have an important contribution from large-scale rotation.} Hence, the linewidths observed in \highz molecular gas structures
on these scales should {\em not} be taken as a direct evidence they are intrinsically more turbulent than those in the local ISM,
and the comparison and interpretation of the dynamics of gas structures with local clouds using e.g., the Larson's relations is non-trivial.
\citet{Behrendt16a} draw a similar conclusion using pc-scale resolution simulation: 
large-scale bulk motions may mimic turbulent velocity dispersion due to  
beam smearing, even though contributions due to self-rotation of each individual sub-MCCs is washed out within the beam.

@@

In the mass-size relation plot (\Fig{MR}), the color of a given MCC darkens to the bottom-left direction as $n_{\rm cut}$ increases.
This makes sense from simply the fact that smaller MCCs have smaller masses.
However, what does it mean for them to lie on the same locus?

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow
an ``internal'' mass-size relation, where $M\propto R^{1.33}$.
%If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond
%to structures with masses and sizes comparable to those of the cores found in regions of high-mass \SF.
%If constant column density (Larson's third law) is truly a fundamental properties of molecular clouds,
%one interpretation of this would be the MCCs of \flower are capable of high-mass \SF given that they share similar internal structures as
%regions of massive \SF.
%\MM{And is thus inconsistent with the variation in $\sigma^2/R$ with
%  $\Sigma$.  Effectively, Larson's mass-size relation is a single
%  point on that relationship, at the constant $\Sigma$ value.  }
However, the mass-size relation has been argued as merely an artifact of the narrow range of column densities traced
with a certain tracer (e.g., \citealt{Ballesteros11}).
That is, it is solely a result of $\rho\propto M R^{-3}$.
For instance, \citet{Ballesteros02a} show that the density
of clouds ($\rho$) is independent of their size ($R$) when one properly extract these quantities in three-dimensional space instead of
two-dimensional space; the latter is done in \obs.
When they project the clouds into two-dimensional space and measure the densities and sizes of clouds for a given
line tracer, they find $\rho \propto R^{-1}$, which is unsurprising since $N_H$ is just a constant.
They therefore argue that the mass-size relation is simply a result of $\rho\propto M R^{-3}$
observed in 2D-space at a fixed column density (cf. an actual physical relation of $M \propto R^{4/3}$ claimed in
observational studies). % where $\rho$ would be proportional to $R^{-1/2}$
% since $M$ would then scale as $R^{3}$.
% naturally display a linear relationship in $\log M - \log R$ plot.

% the widespread in density for a given R.
We show the mass-weighted number density-size relation relation of MCCs of \flower in \Fig{n}.
As we increase the density threshold $n_{\rm cut}$, MCCs break into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
Following \citet{Ballesteros02a}'s argument, we expect the density 
of MCCs to be independent of the cloud size (since they are identified in 3D-space).
On the other hand, if the Larson's third relation holds ($M \propto R^{x}$, where $x\in[4/3, 2.5]$; e.g., \citealt{Lombardi10a}),
we expect the density to scale as $n\propto R^{x}$, where $x\in[-1/2, -5/3]$. 
As shown in \Fig{n}, the density of MCCs scales inversely with the MCC size, which would support Larson's relation.

\begin{figure}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/weighted-density_size-pc_ss16}
\caption{Mass-weighted gas density and size of MCCs in the accreting phase of \flower.
At higher $n_{\rm cut}$ (darker color), MCCs are broken into smaller MCCs and
form the cluster of points that are to the top left of the parent MCC identified at a lower density threshold. 
See also \Fig{MR} for the corresponding mass-size relation of MCCs of \flower. 
For consistency of our notation throughout this paper, we show $n$ on the y-axis for density.
\label{fig:n}}
\vspace{0.5em}
\end{figure}

@@

We study the dynamics of MCCs in a \z$\sim$\,6 prototypical galaxy, \flower,
and their temporal evolution using the state-of-the-art cosmological zoom-in simulations (\ncode{Serra}),
which include a chemical network to determine the formation of molecular hydrogen, heating and cooling of the ISM by
UV radiation and metal lines, and detailed stellar feedback.
Properties of \flower are briefly summarized in \Sec{sim}.
We use a three-dimensional clump-finding algorithm to identify MCCs.
We decompose the molecular structures into non-overlapping objects by identifying a set of
density contours with varying densities at multiple evolutionary stages.
Most notably, the accreting phase, starburst phase, and quiescent phase.
We extract properties such as mass, size, Mach number, velocity
dispersion, gas surface density, and virial parameter ($M_{\rm gas}, R, \mathcal{M},
\sigma_{\rm gas}, \Sigma_{\rm gas}, \alpha_{\rm vir}$) for each MCC and perform a Toomre-$Q$ stability analysis on \flower.

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$,
and thus, some of the MCCs within the main disk break into multiple sub-MCCs at higher $n_{\rm cut}$.
The $\sim$200\,pc-scale MCCs found with a low density threshold
correspond to the arms of the disk of \flower and break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
Overall, the mass of MCCs ranges between $10^{5.5-8.5}$\,\Msun, depending on the chosen density threshold.
This mass range is comparable to those observed in \z\ssim2 galaxies in rest-frame UV and optical wavelengths.
Similarly massive molecular structures (few times 10$^7$\,\Msun) have been
reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the
48\,kpc box studied by \citealt{Behrendt16a}).
However, the IGM and merger and accretion histories are not properly modeled in such simulations.
That said, the similar mass range found in MCCs of \flower\ is
reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc).
On the other hand, the gas velocity dispersion $\sigma_{\rm gas}$ is rather insensitive to the adopted density threshold.

@@

MCCs of \flower are found to have velocity dispersion and gas surface density systematically higher than
Milky Way clouds regardless of the density threshold $n_{\rm cut}$ adopted.
These MCCs are, in fact, highly supersonic (with high Mach numbers).
Their velocity dispersions are comparable to those observed in $z$\ssim2 starburst galaxies ($\sigma_{\rm gas}\simeq200$\,\kms); however,
comparing the velocity dispersions of MCCs from bulk motions versus turbulence
indicates that large-scale rotation is an important contributor, even in the
accreting phase of \flower, which displays a highly disturbed morphology.
This poses a challenge to the interpretation of spatially resolved molecular gas structures observed in \highz galaxies to-date.
In particular, any velocity dispersions measured on similar scales as here (even down to $\sim$\,40\,pc)
should {\em not} be taken as a direct evidence that \highz molecular gas structures are intrinsically more turbulent than those in the local ISM,
unless contributions from bulk motions are properly accounted for.
%This means that a lot of the velocity dispersion infer on even the few-tens of parsec scales have a non-negligible contribution
%from rotation (cf. solely random motion). Therefore it is not fair to say that \highz molecular gas ``clumps`` (or whatever name used
%for structures in the literature) are more turbulent based on solely measured velocity dispersion.

@@

% end
Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
While observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial,
we show in this work that prototypical galaxies at the EoR with properties similar to \flower
are expected to have molecular gas structures on sub-kpc scales; however, these are not
the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from
large-scale motions even in a highly disturbed stage.
This means that caution should be taken when interpreting observational data,
albeit the impressive resolution and sensitivity that are unprecedented.
%Careful consideration of large-scale motions is required
%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR.
Thus, with the resolution provided by existing data, it remains unclear whether \highz molecular gas structures 
are truly intrinsically more turbulent than those in the local ISM.
This picture will become clearer as deeper and higher resolution imaging of
molecular gas at \highz are obtained with ALMA and NOrthern Extended Millimeter Array (NOEMA) in the next few years, and 
potentially with the Next Generation VLA (ngVLA) in the 2030s.
On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining
and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
%These predictions can in turn be
%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
%\SF since the cosmic dark ages.
